\section{}
KVS its the Key-Value storage framework which provide high level API for handling `feeds` of the data.
Something about sequential consistency...last operation for the operation.
Features:
Managing linked list
various backend support:leveldb, ring
sequential consistency via feed server
basic schema
extendable schema?
secondary indexes?
mupltiple backends
the application is kind of framework for seq consistency via feed server or something else.
all the operation that are make without secondary indexes,i.e not linked can be used without feed server.
The data in kvs presented as plain scala case classes 

iterators, all records can be chained into double-linked list. so you can inherit from entry class and provide the data type.
kvs use scala pickling library for serialization so the picklers must be defined on compile time for you kind of data.

the table will support add/remove linked list operation.

kvs.entries(kvs.get(feed,users), user, undefined)

kvs.all(user) - real flat values of all keys from table.

containers are just boxed for storing top of lists 

database init kvs.join


put operation is mean put into the database, but add is adding to the list

leveldb - for secondary indexes
consistency - put each in the box


statically typed. mutable, key-value,case class store 
schemas 
for each container loc process should be spawned - handle feed operations ordering and consistency


\section{}

after handler for entries with particular payload is defined
it can be reused for specific tagged type
Scalaz tygged type is used for specify the "new type" from existing type without the needs to actually create the types.


For example the Message and Metrics are the same kind of entry with string payload.
Typicaly they are marked by some empty trait 

trait Msg
trait Mtr

and the tagged types can be created as follows

type Message = En[String] @@ Msg
type Metrics = En[String] @@ Mtr

actually as soon as you defined the En[String] handler implicitly you are ready to define the new handlers.
type tags will help to catch the error about incompatible operations on compile time.
