\subsection*{KVS/RING Data Metrics}

\paragraph{}
Services uses the data storage so its helpfull to track the state of the different data distribution metrics.
The RING distributed key-value storage also provide the node extension to collect and propogate different metrics.

\paragraph{}
These various stats give a picture of the general level of activity or load on the node at specified moment.

\begin{description}
\item [Disk/Memory usage]
Available disk space. Used file descriptors. Swap Usage. IO wait.
\item [Read operations]
Consistent reads coordinated by this node. Number of local replicas participating in secondary index reads.
Number of siblings encountered during all GET operations by this node within the specific time.
\item [Write operations]
Consistent writes coordinated by this node.
Object size encountered by this node within the specific time.
Abnormally large objects (especially paired with high sibling counts) can indicate sibling explosion.
\item [Network]
Throughput metrics. Latency metrics. General load/health metrics. Network errors.
\item [Search]
Documents indexed by search. Search queries on the node. Number of “failed to index” errors Search encountered for specific time.
\item [General Load/Health Metrics]
Watch for abnormally high sibling counts, especially max ones.
Number of unprocessed messages in the vnode message queues of the Search subsystem on this node in the specific time.
\end{description}

\paragraph{}
The KVS/RING Metrics Extension provide JMX control over data distribution system.
